Variational Monte Carlo on Bosonic Systems

### 2018-04-05 project_1/article/article.tex
Fought with last figure.
Add spellchecked introduction

    Second, we outline in more detailed algebra the nature of a systems we will
    be studying. For
    the non-interacting system we are able to derive an exact variational energy 
    to which we
    can compare the results from our simulations. We furthermore give a
    description of an interacting system implemented as if each
    particle is a hard sphere.

@@

    Fourth, we put the machinery described in the
    previous sections to work. We test against the actual values in a
    non-interacting system before analysing the more interesting perturbed-trap
    system with interacting particles.

@@

\section{Brute Force Metropolis-Hastings}

    \begin{figure*}
        \makebox[\textwidth][c]{
            \includegraphics[width=1.2\textwidth]{../data/figures/problem_b.pdf}
        }
        \caption{Comparison of analytic and numeric results with the exact
        expression for the energy as a function of $\alpha$. The plots show the
        standard deviation from the blocking method as error ticks. In the
        figure $N$ is the number of particles and $d$ the number of dimensions.}
        \label{fig:initial_problem_b}
    \end{figure*}

@@

>>>>

    Second, we outline in more detailed algebra the nature of the systems we
    will be studying. For the non-interacting system we are able to derive an
    exact variational energy to which we can compare the results from our
    simulations. We furthermore give a description of an interacting system
    implemented as if each particle is a hard sphere.

@@

    Fourth, we put the machinery described in the previous sections to work. We
    test against the actual values in a non-interacting system before analyzing
    the more interesting perturbed-trap system with interacting particles.

@@

@@

\clearpage
\onecolumngrid
\section{Brute Force Metropolis-Hastings}
    \begin{figure}[b]
        \makebox[\textwidth][c]{
            \includegraphics[width=1.2\textwidth]{../data/figures/problem_b.pdf}      
        }
        \caption{Comparison of analytic and numeric results with the exact
        expression for the energy as a function of $\alpha$. The plots show the
        standard deviation from the blocking method as error ticks. In the
        figure $N$ is the number of particles and $d$ the number of dimensions.}
        \label{fig:initial_problem_b}       
		\vspace{2cm}
    \end{figure}
